NEED TITLE

### 2015-01-13 ms.tex
Work on intro

\section{Analytic Expectations}

Recently, Murray \& Chang (2014) considered the spherical collapse of isothermal turbulently supported gas accounting for adiabatic heating from compression of the turbulence. In particular,  {\bf SHOW EQUATIONS}
Their basic results are that the run of density asymptotes to 
\be
\rho(r,t)=
\begin{dcases}
\rho(r_0)\left({r\over r_0}\right)^{-3/2}, & r<r_*\\
\rho(R,t)\left({r\over R}\right)^{-k_\rho}, \ k_\rho\approx1.6-1.8 & r>r_*.
\end{dcases}
\ee
Since $k_\rho$ is fairly close to $1.5$ at all radii, taking $r_0=R$
is a fair approximation. 
The infall velocity 
%
\be
u_r(r,t)=
\begin{dcases}
-\Gamma\sqrt{GM_*(t)\over r}, \sim r^{-1/2} & r<r_*\\
-\Gamma\sqrt{GM(r,t)\over r} \sim r^{0.2} & r>r_*,
\end{dcases}
\ee
%
where $\Gamma \approx 0.7$ at small radii, and $\Gamma\approx 1.0$ at
large radii.

@@

@@

The comparative plots for the less massive region are shown in \ref{fig:132_002_graphs}.  The upper left graph shows a slice perpendicular to the z axis in the plane of peak density.  The graph shows a single filamentary strand of accretion towards the inner disk-like structure.

Here again the top right plot shows $\rho(r)$ alongside lines of $r^{-3/2}$, $r^{-2}$ and $r^{-5/2}$.  In this instance, however, the slope of $\rho(r)$ is approximately $r^-2$ for $r \gtrsim 0.1$ pc as well as for $r \lesssim 5e-3$ pc.  Between radii $r \eqsim 0.01$ pc and $r \eqsim 0.1$ pc, $\rho$ closely matches the slope of $r^{-3/2}$.  There is also a sharp spike in density at $r = 6e-3$ pc that is notable in the mass plot as well.

>>>>

The rapid formation of stars remains an unsolved problem in astrophysics.

Here we will focus on the physics of rapid star formation and accretion.  An early model of Shu (1977) estimated the accretion rate onto stars by 
assuming that stars form from hydrostatic cores
supported by thermal gas pressure. The accretion
rate in his model was independent of time, given
by $M = m0c_s^3/G$, where $c_s$  is the
sound speed in molecular gas, and $m_0 = 0.975$.
Shu (1977) predicted a maximum accretion rate was $yr^{-1}$, which is too small to explain
the origin of massive stars.

Later workers overcame the difficulty with the accretion rate by adopting the turbulence speed in lieu of the sound speed (Myers \& Fuller 1992, McLaughlin \& Pudritz 1997, McKee \& Tan 2003). In doing so they were able to replace the slower signal speed of sound with the faster turbulent speed.  However, they rely on assuming that a hydrostatic core supported by turbulent pressure is the initial condition and that turbulence is static and unaffected by the collapse.

Recently Murray \& Chang (2015) developed a 1-D model of spherical collapse that treat turbulence as a dynamical variable and does not assume that the initial condition is a hydrostatically supported region.  They were able to accomplished this by taking advantage of the recent results of Robertson \& Goldreich (2012) on compressible turbulence.   In particular

{\bf need equation}

Hence, this allowed MC15 to include an energy equation for the turbulent velocity that alongside the equations for mass continuity and momentum gives a set of equations that can be solved in spherical symmetry numerically.  In addition, they were able to analytically show that the results of their calculations gave density and velocity profiles that appear to be in line with both recent numerical calculations (Lee et al 2015) and observations.

In particular, their basic results are that the run of density asymptotes to 
\be
\rho(r,t)=
\begin{dcases}
\rho(r_0)\left({r\over r_0}\right)^{-3/2}, & r<r_*\\
\rho(R,t)\left({r\over R}\right)^{-k_\rho}, \ k_\rho\approx1.6-1.8 & r>r_*.
\end{dcases}
\ee
Since $k_\rho$ is fairly close to $1.5$ at all radii, taking $r_0=R$
is a fair approximation. 
The infall velocity 
%
\be
u_r(r,t)=
\begin{dcases}
-\Gamma\sqrt{GM_*(t)\over r}, \sim r^{-1/2} & r<r_*\\
-\Gamma\sqrt{GM(r,t)\over r} \sim r^{0.2} & r>r_*,
\end{dcases}
\ee
%
where $\Gamma \approx 0.7$ at small radii, and $\Gamma\approx 1.0$ at
large radii.

@@

These results compared favorable with the results of numerical simulations (Lee et al. 2015).  However, it is unclear if the results of

@@

The comparative plots for the less massive region are shown in \ref{fig:132_002_graphs}.  The upper left graph shows a slice perpendicular to the z axis in the plane of peak density around this region of star formation.  The graph shows a single filamentary strand of accretion towards the inner disk-like structure.

Here again the top right plot shows $\rho(r)$ alongside lines of $r^{-3/2}$, $r^{-2}$ and $r^{-5/2}$.  Between $0.01\,{\rm pc} \lesssim r \lesssim 0.1$ pc, $\rho$ closely matches the slope of $r^{-3/2}$.  This same region shows a flattening in the mass profile (middle right plot) and a radial velocity profile that is similar to $r^{-1/2}$ (middle left plot).  This region also shows flat $\dot{M}$ profile (lower left plot).  For larger radii, the density profile shows a break toward a steeper power law in $r$ and the velocity profiles shows a switch to rising with $r$ rather than falling with $r$.  The mass profile shows a continued monotonic increase with $r$, indicating that the mass is dominated by the gas and not by a central mass.

In addition, a sharp spike in density appears at $r = 6e-3$ pc that is notable in the velocity, mass, and $\dot M$, plots as well.  The plot of moments of inertia also indicate that this point is where the two particles begin to diverge most significantly.

The middle left plot shows the velocity profiles, which also indicate an anomoly at $r \eqsim 6e-3$ pc.  However, the general trend of both turbulent and radial velocity is increasing inward from $r \eqsim 0.1$ pc, and also increasing outward from $r \eqsim 0.1$ pc.

The mass distribution, the middle right plot, again increases monotonically.  The flattening in this less massive region occurs at the notable radius of $r \eqsim 6e-3$ pc, before steepening again.
